\textbf{ Joystream: A Protocol for User Governed Content Platforms }

### 2019-02-25 paper.tex
Fix typo
Last commit reformats; let's not do that. Makes the diff easier to read.
Presumably, "silten" is meant to be "silent"?

Constant values are displayed with capitalized snake case as follows: {\tiny FOO\_BAR}. These are values which cannot be changed through governance, and require a hard for or consensus upgrade. On some occasions the symbol {\tiny C} will be used to denote some constant which is specific to the context.

@@

The Joystream protocol is stateful, and the infrastructure for the secure distribution and updating of this state is a blockchain system.
A given instantiation of the Joystream protocol runs on its own single purpose blockchain infrastructure, which only processes transactions related to this instantiation. In the rest of the document this blockchain will be treated as a silten transaction ordering mechanism, but in what follows it is briefly described what assumptions are made about the blockchain infrastructure in the protocol design. In what follows, and in the rest of the document, the \textit{platform or platform state} will refer to the state upon which transactions operate. In Bitcoin, this would for example be the UTXO set. This would be as distinct from the state of the underlying blockchain infrastructure itself, namely the actual chain of blocks designated by the chain selection rule.

>>>>

Constant values are displayed with capitalized snake case as follows: {\tiny FOO\_BAR}. These are values which cannot be changed through governance, and require a hard fork or consensus upgrade. On some occasions the symbol {\tiny C} will be used to denote some constant which is specific to the context.

@@

The Joystream protocol is stateful, and the infrastructure for the secure distribution and updating of this state is a blockchain system.
A given instantiation of the Joystream protocol runs on its own single purpose blockchain infrastructure, which only processes transactions related to this instantiation. In the rest of the document this blockchain will be treated as a silent transaction ordering mechanism, but in what follows it is briefly described what assumptions are made about the blockchain infrastructure in the protocol design. In what follows, and in the rest of the document, the \textit{platform or platform state} will refer to the state upon which transactions operate. In Bitcoin, this would for example be the UTXO set. This would be as distinct from the state of the underlying blockchain infrastructure itself, namely the actual chain of blocks designated by the chain selection rule.
